Automated Verification and Synthesis of Cyber-Physical Systems: Advances and Challenges

### 2018-03-12 paper.tex
updated title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Automated Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges}

@@

%--------------------------------------
\section{Automated Verification and Synthesis of Cyber-physical systems}
\label{sec:model}
%--------------------------------------

@@

Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuit-implementations or programs with loops, whose bounds are too large or cannot be statically determined. Indeed, such an issue has pushed researchers to overcome the depth limitation and propose extensions capable of proving global correctness. \textcolor{blue}{In particular, we can adopt two possible strategies to prove properties using BMC: \textit{(i)} compute the \textit{completeness threshold}, which can be smaller than or equal to the maximum number of loop-iterations occurring in the program or \textit{(ii)} determine the high-level worst-case execution time (WCET), which also gives a bound on the maximum number of loop-iterations~\cite{handbook09,ckso04,Ganai08}. However, in practice, complex software systems involve large data-paths and complex expressions. Therefore, the verification conditions that arise from BMC of programs become harder to solve and require substantial amounts of memory to build. Finally, another strategy is to use a complementary technique, with the potential to fill the gap between the adopted depth and all subsequent ones, such as induction, which is explained below.} \textcolor{red}{colocar uma ref}.

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Automated Verification and Synthesis of Cyber-Physical Systems: Advances and Challenges}

@@

%--------------------------------------
\section{Automated Verification and Synthesis of Cyber-Physical Systems}
\label{sec:model}
%--------------------------------------

@@

Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuit-implementations or programs with loops, whose bounds are too large or cannot be statically determined. Indeed, such an issue has pushed researchers to overcome the depth limitation and propose extensions capable of proving global correctness. \textcolor{blue}{In particular, we can adopt two possible strategies to prove properties using BMC: \textit{(i)} compute the \textit{completeness threshold}, which can be smaller than or equal to the maximum number of loop-iterations occurring in the program or \textit{(ii)} determine the high-level worst-case execution time (WCET), which also gives a bound on the maximum number of loop-iterations~\cite{handbook09,ckso04,Ganai08}. However, in practice, complex software systems involve large data-paths and complex expressions. Therefore, the verification conditions that arise from BMC of programs become harder to solve and require substantial amounts of memory to build. Finally, another strategy is to use a complementary technique, with the potential to fill the gap between the adopted depth and all subsequent ones, such as induction, which is explained below~\cite{EenS03,Sheera00}.}
